Mitigating DDoS attacks in Named Data Networking

### 2012-11-28 paper.tex
Adding temporary abstract and small title modification (used for paper registration)
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@825 df1a90cd-247b-4364-bdaf-287a704eb499

\documentclass[conference]{IEEEtran}
\title{Mitigating (D)DoS in Named-Data Networking}%:\\ Cache/Content Poisoning}
\author{anonymous}

@@

\begin{abstract}
%
abstract
%
\end{abstract}

>>>>

\documentclass[conference]{IEEEtran}
\title{Mitigating DDoS attacks in Named Data Networking}%:\\ Cache/Content Poisoning}
\author{anonymous}

@@

\begin{abstract}
%
Distributed Denial of Service attack is a major problem on the existing Internet.
Named Data Networking (NDN) is a future Internet architecture that makes most existing DDoS attack infeasible.
At the same, NDN may be vulnerable to NDN-specific attacks, such as Interest flooding attack. 
This paper presents a simulation-based study on effects of Interset flooding DDoS attack, as well as study of a number of DDoS-attack prevention algorithms that can be implemented on NDN routers.
The presented results give evidences that flooding-based attacks have much less effective in NDN than in the current Internet, as well as that inherent flow-balance property of NDN (i.e., one Interests brings at most one Data) can be used as a basis for effective DDoS mitigation algorithms. 
%
\end{abstract}
